\documentclass[11pt,a4paper]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{fontspec}
\usepackage{tabularx}
\usepackage{array}

% Set main font - Classic serif font for professional appearance
\usepackage{lmodern}
\usepackage[T1]{fontenc}
% Use Roman (serif) as default - removes the \sfdefault which was making it sans-serif

% Configure hyperlinks
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
    pdftitle={Galileo Sanchez - Resume},
    pdfauthor={Galileo Sanchez}
}

% Define colors
\definecolor{darkgray}{gray}{0.2}
\definecolor{mediumgray}{gray}{0.5}
\definecolor{lightgray}{gray}{0.8}

% Remove page numbers
\pagestyle{empty}

% Custom section formatting
\titleformat{\section}
  {\large\bfseries\color{darkgray}}
  {}
  {0em}
  {}[\textcolor{lightgray}{\titlerule[0.8pt]}]

\titleformat{\subsection}
  {\normalsize\bfseries}
  {}
  {0em}
  {}

% Reduce spacing
\titlespacing*{\section}{0pt}{1.5em}{0.8em}
\titlespacing*{\subsection}{0pt}{1em}{0.5em}

% Custom list formatting
\setlist[itemize]{leftmargin=1.2em, topsep=0pt, itemsep=3pt, parsep=0pt}

% Custom commands
\newcommand{\cvheader}[5]{
  \begin{center}
    {\Huge \textbf{#1}}\\[0.4em]
    {\Large \textcolor{darkgray}{#2}}\\[1em]
    
    \textcolor{mediumgray}{#3}\\[0.6em]
    
    \begin{tabular}{c}
      \href{mailto:#4}{#4} $\bullet$ \href{https://#5}{#5}\\[0.3em]
      \href{https://github.com/galileopy}{github.com/galileopy} $\bullet$ 
      \href{https://www.linkedin.com/in/galileopy}{linkedin.com/in/galileopy}
    \end{tabular}
  \end{center}
  \vspace{1.2em}
}

\newcommand{\cvcompany}[3]{
  \subsection{#1 \textcolor{mediumgray}{#2}}
  #3
  \vspace{0.5em}
}

\newcommand{\cvrole}[4]{
  \textbf{#1} \hfill \textcolor{mediumgray}{\small #2}\\
  \textit{#3}
  \begin{itemize}
    #4
  \end{itemize}
  \vspace{0.4em}
}

\newcommand{\cveducation}[4]{
  \subsection{#1}
  \textbf{#2} \hfill \textcolor{mediumgray}{\small #3}
  \begin{itemize}
    \item #4
  \end{itemize}
}

\begin{document}

% Header
\cvheader{Galileo Sanchez}{Lead Backend Engineer}{Remote, based in Asunción, Paraguay}{galileo@galileopy.com.py}{cv.galileopy.com.py}

% About/Summary
\section{About}
Action-oriented backend engineer with 10+ years of experience building scalable systems and optimizing engineering workflows. I specialize CI/CD automation, event-driven microservices, and developer tooling. My work consistently improves deploy speed, feedback loops, and platform reliability—whether refactoring legacy code into composable services or instrumenting pipelines with clear performance metrics. I thrive in environments with clear goals, collaborative iteration, and freedom to experiment.

% Work Experience
\section{Experience}

\cvcompany{Glui}{-- \textit{U.S.-based startup}}{
  \cvrole{Lead Technologist}{Feb 2025--Present}{Remote}{
    \item Led CI/CD and observability stack design; shipped test-context SDKs and custom tooling for test environments.
    \item Guided and oversaw k6 load testing to validate event capturing setup up to 80M requests/day.
  }
  
  \cvrole{Lead Backend Engineer}{Oct 2024--Feb 2025}{Remote}{
    \item Built 15-minute deployment pipeline via GitHub Actions, Docker, Cycle.io.
    \item Deployed Keycloak for centralized auth; managed observability and resilience.
    \item Delivered core backend services using NestJS for a real-time marketplace.
  }
  
  \cvrole{Software Engineer}{May 2024--Sep 2024}{Remote}{
    \item Created container-based CI pipelines and deployment flows with fast feedback cycles.
    \item Drove service modularization and platform reliability improvements.
  }
}

\cvcompany{Clipboard Health}{-- \textit{U.S.-based marketplace}}{
  \cvrole{Senior Software Engineer}{Dec 2022--Nov 2023}{Remote}{
    \item Migrated invoicing to event-driven microservices, reducing processing time from 2 days to 2 hours.
    \item Led debugging of CDC performance issues and live-stream bottlenecks.
    \item Instrumented and iterated k6 load testing to optimize delivery workflows.
  }
  
  \cvrole{Software Development Engineer}{Nov 2021--Feb 2023}{Remote}{
    \item Extracted React front-end from monolith into standalone repo. With 0 downtime for over 100 collaborators.
    \item Refactored low-code invoicing logic into maintainable services.
  }
}

\cvcompany{Jijo}{-- \textit{U.S.-based startup}}{
  \cvrole{Software Engineer}{2021}{Remote}{
    \item Developed Stripe payments, class booking UI, and conference integration using Chime SDK.
    \item Delivered complete feature flows in weekly iterations with autonomy.
  }
}

\cvcompany{National Computing Center}{Asunción, Paraguay}{
  \cvrole{Full Stack Software Engineer}{2018--2020}{In-Office}{
    \item Built React-based personnel tracking platform for 500+ users.
    \item Fully owned feature delivery and compliance workflows.
  }
}

\cvcompany{Trivellini Tech}{Asunción, Paraguay}{
  \cvrole{Software Engineer}{2017--2018}{In-Office}{
    \item Built real-time Qt/C++ UI for surgical device monitors with responsive protocol layer.
    \item Worked closely with hardware teams on cross-functional integration.
  }
}

\cvcompany{Freelance}{Asunción, Paraguay}{
  \cvrole{Full Stack Developer}{2014--2017}{Remote}{
    \item Created Electron/React Shopify label generator.
    \item Delivered backend services, UIs, and integrations using Django and AngularJS.
  }
}

% Education
\section{Education}

\cveducation{National University of Asunción}{Software Engineering}{2009--2013}{Completed core CS curriculum (excluding advanced mathematics). Focus on software development, algorithms, and backend systems.}

% Core Technical Skills
\section{Core Technical Skills}

\textbf{Languages \& Frameworks:} TypeScript, JavaScript, React/Next.js, Node.js, NestJS, C++/Qt\\[0.4em]
\textbf{Systems \& Infra:} Docker, AWS (ECS, RDS, SQS, EventBridge), Terraform\\[0.4em]
\textbf{Testing \& CI:} GitHub Actions, k6, CDC pipelines, end-to-end automation\\[0.4em]
\textbf{Databases:} PostgreSQL, Aurora RDS, CouchDB\\[0.4em]
\textbf{Monitoring:} Datadog, custom logging, runtime metrics\\[0.4em]
\textbf{Payments:} Stripe integrations, event-based pricing logic

% Strengths & Work Philosophy
\section{Strengths \& Work Philosophy}

\begin{itemize}
  \item Biased toward action: quick iteration cycles and small wins that compound
  \item Deep focus on fast feedback loops and system observability
  \item Comfortable owning CI/CD and system plumbing work others avoid
  \item Thrive when collaborating with thoughtful PMs and clear goals
  \item Struggle with premature planning, vague deliverables, or performative coordination
  \item Seek ownership over implementation, not politics or layers of indirection
\end{itemize}

\end{document}